Psyc 601 Multivariate Statistics Project

### 2013-08-14 writeups/proposal/proposal.tex
foo
Former-commit-id: 8ae3fc4d2620b8820a1c7a17b9ac8f0b53caf144 [formerly 487d92856600e556c04fa355aa241cc9b40c21ce]
Former-commit-id: 98822d95e69a2e68a970ac75d6307df0c87dacae

% If the toc is too detailed, try limiting the depth of printed sections in the TOC:
% \setcounter{tocdepth}{2}

@@

\subsubsection{Single-User-Focused Hashtag Modeling}

@@

\subsubsection{Task Domain}

@@

\subsubsection{Recommending Twitter Users to Follow}

@@

\section{ACT-R Declarative Memory Theory}

@@

\subsection{ACT-R DM Model}

\subsection{Connection to Pointwise Mutual Information}

@@

\subsection{Scaling the Equations}

@@

\section{Latent Semantic Analysis Memory Theory}

@@

\subsection{Singular Value Decomposition}

\subsection{Word Order}

\subsection{Scaling Issues}

@@

\section{Vector-Based Memory Systems}

@@

\subsection{Addressing Word Order}

\subsection{Addressing Scalability}

\subsection{BEAGLE}

@@

\subsection{Random Permutations}

@@

\subsection{Comparison between BEAGLE and Random Permutations}

@@

\subsection{Connection to LSA}

@@

\section{Comparison of Vector-based Models and ACT-R}

@@

\section{Incorporating Hashtag Recency}

\subsection{ACT-R}

@@

\subsection{Vector-based Models}

@@

\subsection{Analyses}

@@

TODO: Use stackoverflow and twitter dataset

@@

TODO: Use twitter dataset only for ACT-R

@@

TODO: vector-based and act-r head to head on twitter
TODO: head to head on stackoverflow

\subsubsection{User-customized Hashtag Prediction}

>>>>

% If the toc is too detailed, try limiting the depth of printed sections in the TOC:
\setcounter{tocdepth}{2}

@@

\subsubsection{Modeling Hashtag Creation for a Single User}

@@

\subsubsection{Adding Word-Order Information When Predicting Hashtags}

TODO: speak generally about how word order might be useful for hashtags

\subsubsection{StackOverflow and Twitter Task Domains}

@@

\subsubsection{Recommending Followers on Twitter}

@@

\subsection{ACT-R Declarative Memory Theory}

@@

\subsubsection{ACT-R DM Model}

\subsubsection{Connection to Pointwise Mutual Information}

@@

\subsubsection{Scaling the Equations}

@@

\subsection{Latent Semantic Analysis Memory Theory}

@@

\subsubsection{Singular Value Decomposition}

\subsubsection{Word Order}

\subsubsection{Scaling Issues}

@@

\subsection{Vector-Based Memory Systems}

@@

\subsubsection{Addressing Word Order}

\subsubsection{Addressing Scalability}

\subsubsection{BEAGLE}

@@

\subsubsection{Random Permutations}

@@

\subsubsection{Comparison between BEAGLE and Random Permutations}

@@

\subsubsection{Connection to LSA}

@@

\subsection{Comparison of Vector-Based Models and ACT-R}

@@

\subsection{Incorporating Hashtag Recency}

\subsubsection{ACT-R}

@@

\subsubsection{Vector-Based Models}

@@

\subsection{Experiments}

@@

TODO: Use stackoverflow and twitter popular-users dataset

@@

TODO: Use twitter common-hashtags dataset only for ACT-R

@@

TODO: vector-based and act-r head to head on twitter common-hashtags
TODO: head to head without word order on twitter common-hashtags
TODO: head to head on stackoverflow

\subsubsection{User-Customized Hashtag Prediction}

TODO: head to head on twitter popular-users dataset
TODO: head to head on stackoverflow
